---
title: "ishratc_OriginalHomeworkCode_04"
author: "Ishrat Chowdhury"
date: "October 23, 2019"
output: html_document
---
Problems:

1. I could not combine my fucntions, so I currently have 3 fucntions, One creating a z stat, one for the p stat, and showing normality
2. I was not sure how to go about getting the confidence interval, I had trouble doing this by hand so was lost.
3. was not able to put the legend on after putting the 90% ci lines
4. would you suggest using a test to figure out whihc model is better
5. i think there are more ways to check if part 1 is normal



1. Write a simple R function, Z.prop.test(), that can perform one-sample Z-tests for proportion data

getting the z stat

```{r}
z.prop.test<-function(p1, n1, p0, CI, p2=NULL, n2=NULL,  alternative="two-sided")
{
if(p1 == 0) {
return (0)
} else {
return ((p1 - p0 ) / sqrt((p0 * (1-p0))/n1))
}
}

```

```{r}
z.prop.test(p1=.33, n1=60, p0=.21, p2=NULL, n2=NULL,  alternative="two-sided", CI=.95)
```

getting the p stat

```{r}
pz.prop.test<-function(p1, n1, p0, conf.level, p2=NULL, n2=NULL,  alternative="two-sided")
{
if(conf.level == .95) {
return (1.96)
} else {
return ("sorry")
}
}
```

```{r}
pz.prop.test(p1=.33, n1=60, p0=.21, conf.level =.95, p2=NULL, n2=NULL,  alternative="two-sided")
```

checking for normality

```{r}
chz.prop.test<-function(p1, n1, p0, conf.level, p2=NULL, n2=NULL,  alternative="two-sided")
{
if((p0 * n1)>5)  {
return ("normal")
} else if(((1-p0) * n1)>5)  {
return ("normal")
}  else {
return ("not normal")
}
}
```

```{r}
chz.prop.test(p1=.33, n1=60, p0=.21, conf.level =.95, p2=NULL, n2=NULL,  alternative="two-sided")
```

2. The dataset from Kamilar and Cooper has in it a large number of variables related to life history and body size. For this exercise, the end aim is to fit a simple linear regression model to predict longevity (MaxLongevity_m) measured in months from species' brain size (Brain_Size_Species_Mean) measured in grams. Do the following for both longevity~brain size and log(longevity)~log(brain size):

first load the dataset

```{r}
library(curl)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, stringsAsFactors = FALSE)
attach(d)
head(d)
```
 
make scatterplot 
 
```{r}
library(ggplot2)
?geom_text
?ggplot
g<- ggplot(d, aes(Brain_Size_Species_Mean, MaxLongevity_m))
g<-g+geom_point()
m<-lm(MaxLongevity_m ~ Brain_Size_Species_Mean, data = d)
m #linear regression model
summary(m)
g<-g+geom_smooth(method = "lm", formula = y ~ x)
g
?geom_text
a<-signif(coef(m)[1], digits = 3)
b<-signif(coef(m)[2], digits = 3)
textlab <- paste("y = ",b,"x + ",a, sep="")
textlab
g<-g+geom_text(aes(x = 245, y = 30, label = textlab), color="black", size=5, parse = FALSE)
g

```

the intercept is 248.95 and the slope is 1.22 (B1). The p value for this is very small and therefore significant, which is also known by the three start code. We reject the null hypothesis.

compute ci for slope

```{r}
ci <- confint(m, level = 0.9)  # using the results of lm()
ci
al<-signif((ci)[1], digits = 3) # lower bound
bl<-signif((ci)[2], digits = 3)
au<-signif((ci)[3], digits = 3) # upper bound
bu<-signif((ci)[4], digits = 3)
g<-g+geom_abline(intercept = al, slope = bl, color="red")+geom_abline(intercept = au, slope = bu, color="red", show.legend = TRUE)
?geom_abline
g<-g+theme(legend.position = "bottom")
g

```

point estimate

```{r}
brainweight=800
longevity=a+b*brainweight
longevity
```

no do it all for log

```{r}

d$logMaxLongevity_m <-log(d$MaxLongevity_m)
d$logBrain_Size_Species_Mean <-log(d$MaxLongevity_m)

gl<- ggplot(d, aes(logBrain_Size_Species_Mean, logMaxLongevity_m))
gl<-gl+geom_point()
ml<-lm(logMaxLongevity_m ~ logBrain_Size_Species_Mean, data = d)
ml #linear regression model
summary(ml)
gl<-gl+geom_smooth(method = "lm", formula = y ~ x)
gl
?geom_text
alog<-signif(coef(ml)[1], digits = 3)
blog<-signif(coef(ml)[2], digits = 3)
textlablog <- paste("y = ",blog,"x + ",alog, sep="")
textlablog
gl<-gl+geom_text(aes(x = 7, y = 8, label = textlablog), color="black", size=5, parse = FALSE)
gl
```

this is definately not the right model because it is a perfect model


```{r}
cil <- confint(ml, level = 0.9)  # using the results of lm()
cil
allog<-signif((cil)[1], digits = 3) # lower bound
bllog<-signif((cil)[2], digits = 3)
aulog<-signif((cil)[3], digits = 3) # upper bound
bulog<-signif((cil)[4], digits = 3)
gl<-gl+geom_abline(intercept = allog, slope = bllog, color="red")+geom_abline(intercept = aulog, slope = bulog, color="red", show.legend = TRUE)
gl

```

point estimate

```{r}
brainweightlog=800
longevitylog=alog+blog*brainweightlog
longevitylog
```
